Reduced plasticity and opportunity for selection in terrestrial ectotherm populations under climate change

### 2023-03-17 ms.qmd
Added some jazz about PB, fixed figure in supp.

### *Sensitivity Analyses*
### *Publication Bias*

@@

  ggsave(p3, filename = "./output/figures/figS1.pdf", width = 10, height = 8)

>>>>

### *Publication Bias*

We explored the possibility for publication bias graphically, using funnel plots, and more formally by including in our meta-regression models sampling varinace and publication year [@Nakagawa2021-uf]. Funnel plot asymetry may suggest a 'file-drawer' form of publication bias whereby low-powered studies are less likely to be published. However, asymetry can also result form high hetereogenity. As such, testing (and correcting) for publication bias using a meta-regression approach can attempt to counteract bias that maybe driven by high hetereogneity. In addition, time-lag bias is very common, whereby effect magnitude declines through time with the publication of more studies, often of higher power [@Yang2022-qw].

@@

  ggsave(p3, filename = "./output/figures/figS1.pdf", width = 11.5, height = 8)
